Compositional equivalences based on Open pNets

### 2020-02-05 2016-Weak-FH-Bisim/WeakBisim.tex
figure SPImplOpen
ajout figure SPSpecWeakOpen

\begin{figure}[ht]
   \centerline{\includegraphics[width=11cm]{ATG/SPSpecOpen}}
   \caption{Specification OA}
   \label{SimpleProtCounter:SpecOA}
\end{figure}

\begin{figure}[ht]
   \centerline{\includegraphics[width=10cm]{XFIG/SPSpecOpen}}
   \caption{Specification OA}
   \label{SimpleProtCounter:SpecOA}
\end{figure}

@@

    \begin{figure}[ht]
  \centerline{\includegraphics[width=10cm]{ATG/SPImplOpen}}
  \caption{Open Automaton of the Simple Protocol Implementation}  \label{SimpleProtCounter:ImplOA}
\end{figure}

@@

  WOT2 here is the transition delivering the result of the algorithm to hole $Q$. Remark that it includes a loop increasing the error counter, occuring before the action of $Q$, and this action is using the resulting value of the counter. Let us go into the details, using rules WT1/2/3.  First WT1 adds a $\tau$ loop on each state. Then consider application of Rule WT3 on a sequence 3 internal actions ``$\tau\subst{ec\gets ec+1};\tau\subst{ec\gets ec+1};\tau$''. Hole actions and predicates are empty, we just concentrate on the Post operations. Rule WT2 transforms each 3 OTs into WOTs. In the drawing we use \texttt{ec++} to abbreviate the Post: $\subst{ec\gets ec+1}$. Then WT3 produces the weak OT:
  $\openrule
         {\{\}, True,
			\subst{\texttt{ec++}\shortotimes\texttt{ec++}\shortotimes\emptyset} }
         {s \OTWeakarrow {\tau\subst{\texttt{ec++}}} s'}$
         that you can rewrite as:      
  $\openrule
         {\{\}, True,
			\subst{ec\gets ec+2} }
         {s \OTWeakarrow \tau s'}$

@@

\begin{figure}[h]
   \centerline{\includegraphics[width=10cm]{ATG/SPSpecWeakOpen}}
  \caption{Weak Open Automaton of the Specification \TODO{out of date}}
   \label{SimpleProtCounter:WeakSpecOA}
\end{figure}

>>>>

%\begin{figure}[ht]
%   \centerline{\includegraphics[width=11cm]{ATG/SPSpecOpen}}
%   \caption{Specification OA}
%   \label{SimpleProtCounter:SpecOA}
%\end{figure}

\begin{figure}[ht]
   \centerline{\includegraphics[width=9cm]{XFIG/SPSpecOpen}}
   \caption{Specification OA}
   \label{SimpleProtCounter:SpecOA}
\end{figure}

@@

    \begin{figure}[ht]
  %\centerline{\includegraphics[width=10cm]{ATG/SPImplOpen}}
  \caption{Open Automaton of the Simple Protocol Implementation}  \label{SimpleProtCounter:ImplOA}
\end{figure}

@@

 WOT2 here is the transition delivering the result of the algorithm to hole $Q$. Remark that it includes a loop increasing the error counter, occurring before the action of $Q$, and this action is using the resulting value of the counter. Let us go into the details, using rules WT1/2/3.  First WT1 adds a $\tau$ loop on each state. Then consider application of Rule WT3 on a sequence 3 internal actions ``$\tau\subst{ec\gets ec+1};\tau\subst{ec\gets ec+1};\tau$''. Hole actions and predicates are empty, we just concentrate on the Post operations. Rule WT2 transforms each 3 OTs into WOTs. In the drawing we use \texttt{ec++} to abbreviate the Post: $\subst{ec\gets ec+1}$. Then WT3 produces the weak OT:
  $\openrule
         {\{\}, True,
			\subst{\texttt{ec++}\shortotimes\texttt{ec++}\shortotimes\emptyset} }
         {s \OTWeakarrow {\tau\subst{\texttt{ec++}}} s'}$
         that you can rewrite as:      
  $\openrule
         {\{\}, True,
			\subst{ec\gets ec+2} }
         {s \OTWeakarrow \tau s'}$

@@

\begin{figure}[h]
   \centerline{\includegraphics[width=15cm]{ATG/SPSpecWeakOpen}}
  \caption{Weak Open Automaton of the Specification \TODO{out of date}}
   \label{SimpleProtCounter:WeakSpecOA}
\end{figure}

\begin{figure}[h]
   \centerline{\includegraphics[width=10cm]{XFIG/SPSpecWeakOpen}}
  \caption{Weak Open Automaton of the Specification}
   \label{SimpleProtCounter:WeakSpecOA}
\end{figure}
